\section{Discussion and Conclusion}
\label{sec:discussion}
\textbf{Limitations.}
We identify several limitations that are important for interpreting our results.

\textit{(1)~Synthetic investigator.} Our expert model assumes a fixed accuracy of $\alpha = 0.85$, which does not reflect the variability of real investigators, including fatigue, differences in experience, or domain specialisation, although the sensitivity analysis (\Cref{sec:exp_sensitivity}) shows that the gains remain even when accuracy drops to $\alpha = 0.70$.

\textit{(2)~Small dataset.} The evaluation is based on 1{,}000 claims, with 200 in the test set (approximately 49 fraud cases), which limits statistical power. Bootstrap confidence intervals between Safe-L2D-Fraud and the confidence baseline overlap, and individual cost and CVaR numbers rest on very few samples. Cross-validation helps to some extent, but the results may still not generalise to production-scale datasets. Evaluation on larger benchmarks (e.g., IEEE-CIS Fraud Detection, European credit card fraud) is an important next step.

\textit{(3)~Inflated fraud rate.} The 24.7\% base rate is much higher than what is typically seen in production, where fraud rates are usually closer to 5--10\%. At lower base rates, the Bayesian posterior would likely concentrate more strongly on the majority class, which could reduce both the sensitivity of the entropy signal and the deferral rate.

\textit{(4)~Conditional independence.} Assumption~A1 (naive Bayes) may underestimate posterior uncertainty when features are correlated. A copula-based KDE could help address this.

\textit{(5)~Hypothesised DAG.} The causal structure is based on domain knowledge rather than learned directly from data. This is deliberate: a practitioner-specified DAG encodes structurally stable relationships that are expected to persist under distribution shift, whereas a data-learned graph would inherit the same transient correlations it is meant to guard against. However, the DAG may be incomplete or contain incorrect edges, and we have not empirically tested sensitivity to DAG misspecification (e.g., adding or removing edges).

\textit{(6)~Simulated OPE.} Our off-policy evaluation uses a simulated behaviour policy rather than real historical decisions, which creates a circularity: the reward model $\hat{r}$ and behaviour policy $\pi_b$ are both learned from the same data, violating the standard OPE assumption that $\pi_b$ is known. So this should be seen as a methodological proof of concept, not as a real-world validation.

\textbf{Robustness to distribution shift.}
Several parts of Safe-L2D-Fraud may be sensitive to distribution shift, which we did not test empirically.

\textit{(7)~Covariate shift on KDE estimates.} The class-conditional densities $\hat{p}(x_k \mid y)$ are estimated from training data. If the feature distribution changes post-deployment, the Bayesian posterior $\pi_F$ can become miscalibrated, causing the entropy signal to over-defer (new legitimate claims look uncertain) or under-defer (new fraud patterns produce confident but wrong posteriors).

\textit{(8)~Prior drift.} The prior $\pi_0$ is fixed from the training set. If the true fraud rate changes over time, that misspecification propagates through every sequential Bayesian update.

\textit{(9)~Adversarial non-stationarity.} Fraud detection operates in an adversarial setting where fraudsters adapt to the deployed system. The DAG's structural advantage is that its \textit{topology}, where features are causally relevant to fraud often is more stable than marginal statistics: a high claim-to-premium ratio remains suspicious even as fraudster tactics evolve. However, the \textit{edge strengths} (how predictive each feature is) can shift as adversaries adapt, and the KDE-based class-conditional densities will not track these changes without retraining. Standard deferral guarantees do not account for this strategic adaptation.

\textit{(10)~Calibration degradation.} Under distribution shift, the isotonic-calibrated probabilities $\sigma_j(g(\xx))$ may become unreliable, causing the confidence branch of the deferral rule to fail silently. Conformal prediction sets offer a more robust alternative under exchangeability.

\textbf{Further limitations.}

\textit{(11)~No online learning.} The deferral policy $r_\tau$ is fixed after training. It does not adapt to new data or learn from investigator feedback. With limited investigator capacity, this becomes a constrained bandit problem that our static framework does not address.

\textit{(12)~Reward misspecification.} The CVaR objective uses 0-1 loss, not the asymmetric costs (FN/FP $\approx$ 5--10$\times$) relevant in deployment. Incorporating asymmetric costs into the CVaR term would require recalibrating $\lambda$ and $\delta$.

\textit{(13)~CVaR sample complexity.} Empirical CVaR is computed on non-deferred claims only. With $\delta{=}0.10$ and $N_r{=}128$ retained samples (after 36\% deferral from $N{=}200$), the tail average rests on only ${\approx}13$ samples. The CVaR gap between Safe-L2D-Fraud (0.923) and the confidence baseline (0.938) is not statistically significant at this sample size.

\textit{(14)~Missing uncertainty baselines.} We did not compare against MC Dropout \citep{gal2016dropout} or deep ensembles \citep{lakshminarayanan2017simple}, which provide deferral signals without the naive Bayes assumption and are well-established in selective prediction.

\textbf{Broader impact.}
Fraud detection systems can have an uneven impact on vulnerable populations. Deferral offers a safeguard by sending ambiguous cases to human review, which may help reduce algorithmic bias. At the same time, the deferral rate must be matched to investigator capacity. Fairness-aware extensions incorporating equalized odds constraints \citep{madras2018predict} are an important direction.

\textbf{Conclusion.}
We introduced Safe-L2D-Fraud, a modular framework that combines a pre-trained classifier with CVaR-guided deferral. On a small benchmark, the system reaches 89.5\% accuracy at 64\% coverage, an 8.5 percentage point gain over XGBoost, though a simpler confidence baseline achieves comparable results with less deferral. The primary contribution is the framework design decoupled, risk-aware deferral with an explicit CVaR knob rather than the empirical margins. Key limitations include small sample size, untested distribution shift, and missing comparisons to modern uncertainty methods. Promising extensions include conformal prediction sets, online deferral with capacity constraints, and asymmetric cost-aware CVaR objectives.
